Evaluation

### 2018-03-20 FlairResearch/Paper.tex
Changed the paper

\paragraph{•}
	Our evaluation looks compare our tool, Flair, against some of the top of the line Android security analysis tools. We have narrowed our focus on four other inter-application analysis tools: COVERT, DidFail, DIALDroid, and SEALANT.

>>>>

\paragraph{•}
	We tested Flair's performance in relation to the following questions:\\
	\textbf{Question 1:} How does Flair compare to other inter-application communication analysis tools in respect to the amount of time it takes to analyze a bundle of applications?\\
	\textbf{Question 2:} How does Flair compare to other tools with respect to the number of applications it fails to analyze?\\
	\textbf{Question 3:} How accurately does Flair analyze vulnerabilities within applications when ran against a bundle of benchmark applications?\\
	\textbf{Question 4:} How does Flair's accuracy in analyzing applicaions compare to other inter-application analysis tools?\\
